---
title: "Portfolio 7"
---

In this portfolio, I will complete my analysis of the diamonds dataset by identifying the "best" linear regression model and comparing the models selected using Adjusted R-squared and AIC. 

#load the data
```{r}
library(ggplot2)
data(diamonds)
head(diamonds)
summary(diamonds)
?diamonds
```

#Linear Regression Model

```{r}
diamonds$color <- factor(diamonds$color, ordered = FALSE)
diamonds$cut <- factor(diamonds$cut, ordered = FALSE)
diamonds$clarity <- factor(diamonds$clarity, ordered = FALSE)
# factors are table, depth, clarity, color, cut, carat
```

```{r}
full_model <- lm(price ~ carat + cut + color + clarity + depth + table, data = diamonds)
summary(full_model)
#Adjusted R-squared:  0.916 
```
#Model Selection Using Stepwise Regression
```{r}
best_model1 <- step(full_model, direction = "both", trace = FALSE)
#This automatically selects the best model based on AIC (Akaike Information Criterion).
summary (best_model1)
# the best model based on AIC includes all the six factors. 
```

#model selection based on Adjusted R-squared
```{r}
model1 <- lm(price ~ carat + cut + color + clarity + depth + table, data = diamonds)
summary(model1)$r.squared
#[1] 0.9160543
```
```{r}
model2 <- lm(price ~ carat + cut + color + clarity + depth , data = diamonds)
summary(model2)$r.squared
#[1] 0.9159463, removed the "table" factor 
```

```{r}
model3 <- lm(price ~ carat + cut + color + clarity  + table , data = diamonds)
summary(model3)$r.squared
#[1] 0.916013, removed the "depth" factor 
```

```{r}
model4 <- lm(price ~ carat + cut + color  + depth + table , data = diamonds)
summary(model4)$r.squared
#[1] 0.871565, removed the "clarity" factor 
```

```{r}
model5 <- lm(price ~ carat + cut  + clarity + depth + table , data = diamonds)
summary(model5)$r.squared
#[1] 0.8971377, removed the "color" factor 
```

```{r}
model6 <- lm(price ~ carat +  color + clarity + depth + table , data = diamonds)
summary(model6)$r.squared
#[1] 0.9149359, removed the "cut" factor 
```

```{r}
model7 <- lm(price ~  cut + color + clarity + depth + table , data = diamonds)
summary(model7)$r.squared
#[1] 0.0718017, removed the "carat" factor 
```
 
 
The best model, determined by Adjusted R-squared, includes all six factors, which aligns with the selection made using the AIC method.


